Parsing Postfix Log Files

### 2009-04-24 doc/logparser-results.tex
Changes made after proofreading the preface and chapters 1-3.

\subsection{Characteristics Of The Input Log Files}

@@

\showgraph{build/graph-average-number-of-rules-tried-per-program}{Mean
number of rules used per log line for each Postfix component over all log
files}{Mean number of rules used per log line for each Postfix component}

@@

\Graphref{Increase in parsing time when not caching compiled regexes graph}
shows the effect that not caching compiled regexes has on parser
performance, with mean and standard deviation in \tableref{Increase in
parsing time when not caching compiled regexes table}.  For typical log
files, the mean increase in parsing time when not caching compiled regexes
is \input{build/include-cached-regexes-vs-discarded-regexes-mean}.  Caching
compiled regexes is probably the single most effective optimisation
possible in \parsername{}, and was quite simple to implement: the framework
compiles each rule's regex when the ruleset is loaded, and uses the
compiled regex instead of the source regex when recognising log lines.  As
seen previously, log files 22 \& 62--68 do not suffer such a large increase
in parsing time when the optimisation is disabled; this is because, on
average, fewer rules are used so fewer regexes are compiled per log line
for those log files.  The increase in parsing time when parsing the first
log file is much greater than for the other log files; again, this is
because every rule's hits field starts at zero, so optimal ordering is less
efficient than usual, the mean number of rules used for each log line is
higher than usual, and more regexes will need to be compiled when
recognising each log line.

\showgraph{build/graph-cached-regexes-vs-discarded-regexes}{Increase in
parsing time when not caching compiled regexes}{Increase in parsing time
when not caching compiled regexes graph}

\showtable{build/include-cached-regexes-vs-discarded-regexes}{Increase in
parsing time when not caching compiled regexes}{Increase in parsing time
when not caching compiled regexes table}

>>>>

\subsection{Characteristics Of The \numberOFlogFILES{} Log Files}

@@

\showgraph{build/graph-average-number-of-rules-tried-per-program}{Mean
number of rules used per log line for each Postfix component over
\numberOFlogFILES{} log files}{Mean number of rules used per log line for
each Postfix component}

@@

\Graphref{Percentage increase in parsing time when not caching compiled
regexes graph} shows the effect that not caching compiled regexes has on
parser performance, with mean and standard deviation in
\tableref{Percentage increase in parsing time when not caching compiled
regexes table}.  For typical log files, the mean increase in parsing time
when not caching compiled regexes is
\input{build/include-cached-regexes-vs-discarded-regexes-mean}.  Caching
compiled regexes is probably the single most effective optimisation
possible in \parsername{}, and was quite simple to implement: the framework
compiles each rule's regex when the ruleset is loaded, and uses the
compiled regex instead of the source regex when recognising log lines.  As
seen previously, log files 22 \& 62--68 do not suffer such a large increase
in parsing time when the optimisation is disabled; this is because, on
average, fewer rules are used so fewer regexes are compiled per log line
for those log files.  The increase in parsing time when parsing the first
log file is much greater than for the other log files; again, this is
because every rule's hits field starts at zero, so optimal ordering is less
efficient than usual, the mean number of rules used for each log line is
higher than usual, and more regexes will need to be compiled when
recognising each log line.

\showgraph{build/graph-cached-regexes-vs-discarded-regexes}{Percentage
increase in parsing time when not caching compiled regexes}{Percentage
increase in parsing time when not caching compiled regexes graph}

\showtable{build/include-cached-regexes-vs-discarded-regexes}{Percentage
increase in parsing time when not caching compiled regexes}{Percentage
increase in parsing time when not caching compiled regexes table}

### 2009-04-24 doc/logparser.tex
Changes made after proofreading the preface and chapters 1-3.

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files, and subsequently in reconstructing the
    actions taken by Postfix when processing mail delivery attempts.  This
    thesis describes the creation of a parser for Postfix log files,
    documenting the architecture developed for this project and the parser
    that implements it, explaining the difficulties encountered and the
    solutions developed, and evaluating the parser on the criteria of
    efficiency and Postfix log file coverage.  The parser stores data
    gleaned from the log files in an SQL database; the gathered data can be
    used to optimise current anti-spam measures, to produce statistics
    showing how effective those measures are, or to provide a baseline to
    test new anti-spam measures against.  The Postfix log file parser needs
    to be very precise and strict when parsing, yet must allow users to
    easily adapt or extend it to parse new log lines, without requiring
    that the user have an in-depth knowledge and understanding of the
    parser's internal workings.  The newly developed architecture is
    designed to make the process of parsing new inputs as simple as
    possible, enabling users to trivially add new rules (to parse variants
    of known inputs) and relatively easily add new actions (to process a
    previously unknown category of inputs).  The parser implemented for
    this project is evaluated on the criteria of efficiency and coverage of
    Postfix log files, demonstrating that the conflicting goals of
    efficiency and accuracy can be balanced, and one need not be sacrificed
    to achieve the other.

>>>>

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files, and subsequently in reconstructing the
    actions taken by Postfix when processing mail delivery attempts.  This
    thesis describes the creation of a parser for Postfix log files,
    documenting the architecture developed for this project and the parser
    that implements it, the difficulties encountered and the solutions
    developed.  The parser stores data gleaned from the log files in an SQL
    database; the gathered data can be used to optimise current anti-spam
    measures, to produce statistics showing how effective those measures
    are, or to provide a baseline to test new anti-spam measures against.
    The Postfix log file parser needs to be very precise and strict when
    parsing, yet must allow users to easily adapt or extend it to parse new
    log lines, without requiring that the user have an in-depth knowledge
    and understanding of the parser's internal workings.  The newly
    developed architecture is designed to make the process of parsing new
    inputs as simple as possible, enabling users to trivially add new rules
    (to parse variants of known inputs) and relatively easily add new
    actions (to process a previously unknown category of inputs).  The
    parser implemented for this project is evaluated on the criteria of
    efficiency and coverage of Postfix log files, demonstrating that the
    conflicting goals of efficiency and accuracy can be balanced, and that
    one need not be sacrificed to achieve the other.
